---
title: "Samsung Project"
author: "O.Ruppelt"
date: "Sunday, September 21, 2014"
output: html_document
---

COnnecting libraries to be used in step5
```{r}
library(plyr)
library(reshape2)
```

Downloading datasets from working directory (datasets should be located in folder Samsung in working directory)

```{r}
y_test <- read.table("~/Samsung/test/y_test.txt", quote="\"")
X_test <- read.table("~/Samsung/test/X_test.txt", quote="\"")
subject_test <- read.table("~/Samsung/test/subject_test.txt", quote="\"")
subject_train <- read.table("~/Samsung/train/subject_train.txt", quote="\"")
y_train <- read.table("~/Samsung/train/y_train.txt", quote="\"")
X_train <- read.table("~/Samsung/train/X_train.txt", quote="\"")
features <- read.table("~/Samsung/features.txt", quote="\"")
activity_labels <- read.table("~/Samsung/activity_labels.txt", quote="\"")
```

Merging data in one piece (Step 1). Subject id and activity id are added in the beginning of dataset 

```{r}
test_data<-cbind(subject_test,y_test,X_test)
train_data<-cbind(subject_train, y_train, X_train)
data<-rbind(test_data,train_data)
```

Step 4 is performing foe convenience of step 2. Features are converted to vector of row names with addition of two columns added earlier

```{r}
data_names<-as.vector(features$V2)
names(data)<-c('Subject','Activity',data_names)
```

Step 2. Only columns that include mean and std are taken into new dataset together with first two variables

```{r}
te<- sort(c(1,2,grep('mean()', names(data)),grep('std()', names(data))))
new_data<-data[,te]
```

Activity labels were sorted in ascending manner by their id, so there was no need to sort it one more time.
New variable contains corresponding activity name. This is Step 4

```{r}
new_data$Activity_name<-activity_labels[new_data$Activity,2]
```

Step 5 uses reshape2 and plyr packages and their respective functions melt and ddply

```{r}
melt_data<-melt(new_data, id = c('Subject','Activity','Activity_name'))
tidy_data<-ddply(melt_data, c('Subject','Activity','Activity_name', 'variable'), summarize, mean = mean(value))
head(tidy_data)
```

Writng results into separate text file tidy_data.txt in your working directory

```{r}
write.table(tidy_data, file = '~/tidy_data.txt', row.names= FALSE)
```